~\\[1in] % hack to put space at top.
\textbf{\Huge Acknowledgments}\\

\noindent 
\par First of all, I would like to express my deepest gratitude to my advisor Gustaaf Brooijmans for his guidance and support through my Ph.D. career. Gustaaf's vision, leadership, and dedication have deeply influenced me. 

\par I'd also like to thank other members of my thesis committee: Norman Christ, Brian Humensky, Georgia Karagiorgi, and Zoltan Haiman for reviewing my thesis and providing very helpful and enlightening comments.


\par I am very grateful for the opportunities to take the physics courses offered by Norman Chris, Allan S. Blaer, Robert D. Mawhinney, Alfred H. Mueller, and Gustaaf Brooijmans, which helped me appreciate the beauty of physics and have laid the foundations for my research work. 

\par I want to thank the Columbia ATLAS group which hosts like a family in my research. In particular, I would like to thank Ines Ocha for helping me get started and provide useful discussions for several projects; John Parson and Michael Tuts provide useful comments during or after the group meetings. I also want to thank all other group members for all the help and fun. I am really into the excellent research group with a very open environment where everyone enjoys sharing their knowledge and experience with each other. 
\par I should also thank my colleagues in the ATLAS collaboration across the whole high energy physics community both from the operation and analysis groups, as well as my friends that I knew from the undergrads who are also doing research at CERN during my stay there.
\par Finally, I would like to express my sincere gratitude to my parents,  my grandparents, my parents in law, and my husband Hua Wei. I am deeply grateful for your unconditional love and support in my pursuit of experimental particle physics. I wouldn't get through all the difficulties and make it today without Hua, especially during this special time. To my beloved maternal grandpa, who retired early to take care of me, I am sorry that I lost you without saying goodbye forever. This thesis is dedicated to all of you. 